---
title: "Data Is Beautiful"
output: 
  html_document: 
    css: styles.css
    theme: united
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE)
library(tidyverse)
library(ggthemes)
library(zoo)

lake_mendota <- read_csv("data/lake_mendota.csv")
```

# Lake Mendota {.tabset .tabset-fade}

An artistic and an informative visualization. Sometimes you can visualize inforamtion in a less useful way to grab the attention and then show the actual information.

## Artistic

The left side offset is given by the number of days since August 30 the bar length is the number of days the lake was frozen over. We have a fancy hover effect as well.


```{r artistic-d3}
d3_options <- list(
  minYear = min(lake_mendota$year)
)

r2d3::r2d3("2018-12.js", 
  css = "styles.css", 
  data = lake_mendota, 
  options = d3_options, 
  height = 640, 
  width = "100%"
)
```

## Scientific

This is my attempt at reproducing and cleaning up the [graph](http://www.aos.wisc.edu/~sco/lakes/mendota-dur.gif) created by University of Wisconsin-Madison.

```{r, fig.width=9, fig.height=7}
lake_mendota %>% 
  group_by(year) %>% 
  summarise(`Annual Values` = sum(days)) %>% 
  ungroup() %>% 
  mutate(`5-yr running means` = rollmean(`Annual Values`, 5, fill = NA)) %>%
  gather("label", "days", - year) %>%
  ggplot(aes(x = year, y = days, color = label)) +
  geom_line() +
  theme_hc() +
  ylim(0, 165) +
  scale_colour_hc() +
  labs(
    x = "Seasons (Ice season begins in autumn of year indicated)",
    y = "Total Duration of Ice in Days",
    color = ""
  ) +
  ggtitle("Duration of Ice on Lake Mendota 1854 to 2018")
```

